FEM Model Analysis

### 2021-01-27 FEM_R/model_analysis.Rmd
More WIP stuff for the AgeUK alamanac validation
Defined multiple new output subpopulations in summary_output_gen. Added these to measures_subpop_ELSA so we can use the summary out for the ageUK validation
Removed a chunk that visualised things based on subpopulations as the subpopulations have now changed

### Baseline Projections by Subpopulation

```{r echo = FALSE}
visProjectedBySubpop <- function(base, cd, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/Scenario_1/') {

  if(cd == 'cancre') {
    dis <- 'Cancer'
  } else if(cd == 'diabe') {
    dis <- 'Diabetes'
  } else if(cd == 'hearte') {
    dis <- 'Heart Disease'
  }

  # Generate varnames
  all <- paste0('p_', cd, '_all')
  # age
  a5564 <- paste0('p_', cd, '_5564')
  a6574 <- paste0('p_', cd, '_6574')
  a7584 <- paste0('p_', cd, '_7584')
  a85p <- paste0('p_', cd, '_85p')

  ageMelt <- base %>%
              select(c('year', a5564, a6574, a7584, a85p)) %>%
              dplyr::rename('55 to 64' = a5564, '65 to 74' = a6574, '75 to 64' = a7584, '85+' = a85p) %>%
              reshape2::melt(id.var = 'year', value.name = 'Prevalence')

  ggplot(data=ageMelt, aes(x=year, y=Prevalence, color = variable)) +
          geom_line() +
          labs(title = dis, x = 'Year', y = 'Prevalence')
}

visProjectedBySubpop(baseline, cd = 'cancre')
visProjectedBySubpop(baseline, cd = 'diabe')
visProjectedBySubpop(baseline, cd = 'hearte')
```

@@

>>>>

@@

mf_list <- tmp(mFEM, fFEM, 65:69)
male <- list(male, mf_list[1])
female <- list(female, mf_list[2])
